Methods paper for erosion

### 2017-10-08 docs/methods/erosion_methods.tex
Changed some things. Worked on tex a little.

@@

@@

\subsubsection{Pressure}

@@

The shear stress, pressure, and drag must also be computed using
quadrature, and this can be interpreted as a post-processing step once
the density function, Stokeslets, and rotlets are computed.  All the
quadrature methods are described in Section~\ref{sec:quadrature}

Once the shear stress is computed, it is used to update the shape of the
bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
eliminate tangling and stretching of the mesh, we use a {\thL}
formulation~\cite{hou-low-she1994} which is described in
Section~\ref{sec:thetaL}.  In this section, we also describe our time
stepping method and two regularization terms that are necessary to
control the curvature of the bodies and to maintain spectral accuracy in
space.

For the shear stress and the pressure, we will use odd-even integration
which achieves spectral accuracy if the integrand is no stronger than
$\bigO(\rho^{-1})$.  Since both these integrands are too strong, the
singularity must be weakened.  This can be done by adding a constant
density function which has no effect on the shear stress and
pressure~\cite{poz1992}.  In particular, the shear stress due to the
double-layer potential is equivalent to
\begin{align*}
  \ssigma^{\DD}(\xx_0) &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      \ssigma(\yy) \, ds_{\yy} \\ 
      &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      (\ssigma(\yy) - \ssigma(\xx_0)) \, ds_{\yy}.
\end{align*}
For the pressure, the double-layer potential is equivalent to
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align*}

@@

@@

In order to regularize boundary evolution, we modify
Eq.~(\ref{eqn:bodyEvolution}) to include a curvature-driven component
(also corrected errors in this equation)
\begin{equation}
\dot{\xx}(t) = \abs{\tau} \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
The curvature term acts to smooth bodies that have high-frequency oscillations.

Simple form for my talk
\begin{equation}
\dot{\xx}(t) = \abs{\tau} \nn + \eps \kappa
\end{equation}

\todo[inline]{Artificial Diffusion} 
\todo[inline]{Gaussian Filter}

>>>>

The shear stress, pressure, and drag must also be computed using
quadrature, and this can be interpreted as a post-processing step once
the density function, Stokeslets, and rotlets are computed.

@@

For the shear stress and the pressure, we will use odd-even integration
which achieves spectral accuracy if the integrand is no stronger than
$\bigO(\rho^{-1})$.  Since both these integrands are too strong, the
singularity must be weakened.  This can be done by adding a constant
density function which has no effect on the shear stress and
pressure~\cite{poz1992}.  In particular, the shear stress due to the
double-layer potential is equivalent to
\begin{align*}
  \ssigma^{\DD}(\xx_0) &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      \ssigma(\yy) \, ds_{\yy} \\ 
      &= \int_{\bd\Omega}K_\ssigma(\xx_0,\yy)
      (\ssigma(\yy) - \ssigma(\xx_0)) \, ds_{\yy}.
\end{align*}

Once the shear stress is computed, it is used to update the shape of the
bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
eliminate tangling and stretching of the mesh, we use a {\thL}
formulation~\cite{hou-low-she1994} which is described in
Section~\ref{sec:thetaL}.

@@

\subsubsection{Pressure}
For the pressure, the double-layer potential is equivalent to
\begin{align*}
  p^\DD(\xx) = -\frac{1}{\pi}\int_{\bd\Omega} \frac{1}{\rho^2}
    \left(I - 2 \frac{\rr \otimes \rr}{\rho^2}\right) 
    \nn \cdot (\eeta(\yy) - \eeta(\xx_0)) \,ds_\yy.
\end{align*}

@@

@@

In this section, we also describe our time stepping method and two
regularization terms that are necessary to control the curvature of the
bodies and to maintain spectral accuracy in space.

@@

In order to regularize boundary evolution, we modify the normal velocity in Eq.~(\ref{eqn:bodyEvolution}) as follows
\begin{equation}
\Vn = \abs{\tau} + \frac{\eps}{\log \left(2\pi/L \right)} \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
Here, $\kappa$ is the curvature, $\eps$ is a small parameter, and $L$ is the total arc length of the body. The second term on the right acts to smooth bodies that have high-frequency oscillations. Since we have subtracted the mean curvature, $2\pi/L$, this term is area-preserving, so that the only material loss is due to the shear stress. We chose the prefactor $\log^{-1} \left(2\pi/L \right)$, so that, for 2D Stokes flow, this term scales the same as shear stress as $L \to 0$. Thus, the relative strength of the smoothing is always the same.

We now introduce the tangent angle, $\theta$, defined through the relation
\begin{equation}
(x_s, y_s) = (\cos \theta, \sin \theta)
\end{equation}
where $s$ is arc length. We also introduce the normalized arc length $\alpha = s / L$. In terms of these new variables, the curvature can be expressed as
\begin{equation}
\kappa = \frac{1}{L} \pderiv{\theta}{\alpha}
\end{equation}
Substitution into Eq.~(\ref{})

\vsp{5}
\todo[inline]{Artificial Diffusion} 
\todo[inline]{Gaussian Filter}
